Paper Analysis

### 2025-04-11 Paper_WriteUp/Paper_Plots.qmd
adding numbers to y-axis in fig2

```{r figure 2}
## Adam's code for this figure

gm_players_elo <- list()
gm_session_lengths <- list()
gm_time_diffs <- list()
gm_time_diffs_10 <- list()

@@

  # get players average elo across all games
  gm_players_elo[[gm_players[i]]] <- mean(c(
    tidy_games_gms$WhiteElo[gm_players[i] == tidy_games_gms$White],
    tidy_games_gms$BlackElo[gm_players[i] == tidy_games_gms$Black]
  ))

@@

log_time_diff_plot_gm <- ggplot(gm_time_diff_df, aes(x = as.numeric(time_diff))) +
  geom_histogram() +
  scale_x_continuous(
    trans = scales::log_trans(),
    breaks = c(1, 60, 300, 3600, 86400, 31536000),
    labels = c("1 sec", "1 min", "5 min", "1 hour", "1 day", "1 year")
  ) +
  xlab("Time Between Games (Log Scale)") +
  geom_vline(xintercept = 300, colour = "red") +
  ylab("Frequency") #+ ggtitle("Time Difference Between Current Game and Previous Game for Amateurs")
fig2a <- log_time_diff_plot_gm + theme_single()

@@

session_length_plot_gm <- ggplot(gm_session_lengths_df, aes(x = session_length)) +
  geom_histogram() +
  scale_x_continuous(
    trans = pseudo_log_trans(sigma = 2.36),
    breaks = c(1, 5, 10, 100),
    labels = c("1 game", "5 games", "10 games", "100 games"),
    limits = c(0, 389)
  ) +
  xlab("Number of Games in a Session (Log Scale)") +
  ylab("Frequency") #+ ggtitle("Number of Games per Session for GMs")
fig2b <- session_length_plot_gm + theme_single()

>>>>

```{r figure 2}
#Adam - revised Apr 11, 2025
#Adding numbers to y-axis

#import data from gm cohort
data_path_gm = paste0(all_data_path[4], "/")
files_gm = list.files(data_path_gm, pattern = ".csv")
lichess_data_gm = files_gm %>%
  map_dfr(~read_player(data_path_gm, .x))

bullet_data_gm = lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0", Variant == "Standard", Event == "rated bullet game")

gm_session_lengths <- list()
gm_time_diffs <- list()
gm_time_diffs_10 <- list()

@@

@@

log_time_diff_plot_gm <- ggplot(gm_time_diff_df, aes(x = as.numeric(time_diff))) +
  geom_histogram() +
  scale_x_continuous(
    trans = scales::log_trans(),
    breaks = c(1, 60, 300, 3600, 86400, 31536000),
    labels = c("1 sec", "1 min", "5 min", "1 hour", "1 day", "1 year")
  ) +
  xlab("Time Between Games (Log Scale)") +
  geom_vline(xintercept = 300, colour = "red") +
  ylab("Frequency") #+ ggtitle("Time Difference Between Current Game and Previous Game for Amateurs")
fig2a <- log_time_diff_plot_gm + theme_single_y()

@@

session_length_plot_gm <- ggplot(gm_session_lengths_df, aes(x = session_length)) +
  geom_histogram() +
  scale_x_continuous(
    trans = pseudo_log_trans(sigma = 2.36),
    breaks = c(1, 5, 10, 100),
    labels = c("1 game", "5 games", "10 games", "100 games"),
    limits = c(0, 389)
  ) +
  xlab("Number of Games in a Session (Log Scale)") +
  ylab("Frequency") #+ ggtitle("Number of Games per Session for GMs")
fig2b <- session_length_plot_gm + theme_single_y()
